% LaTeX file for resume
% This file uses the resume document class (res.cls)
% Written by Christian Gati - 10-01-2013
% Updated October 2014

\documentclass[margin]{res}
% === Packages ===
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font
\usepackage{enumitem}
\usepackage{hyperref}

\topmargin=-0.5in % start text higher on the page
\setlength{\textheight}{10in} % increase text height to fit resume on 1 page

\begin{document}
\name{CHRISTIAN GATI}
\address{ 	\centerline{14300 Avalon Reserve Blvd. Apt. 101}	\\
			\centerline{Orlando, FL 32828}					\\
			\centerline{(954) 247 - 4714}						\\
			\centerline{\href{mailto:christian@cgati.com}{christian@cgati.com}}}

\begin{resume}
\section{OBJECTIVE}
			To obtain a position for relevant experience in the field of Computer Science.

\section{EDUCATION}
			University of Central Florida, Orlando, FL	\\
			Bachelor of Science in Computer Science, expected December 2014

\section{EMPLOYMENT}
            \begin{tabular}{p{3in} r}
                University of Central Florida, Orlando, FL & August 2014 - Present
            \end{tabular}
            \begin{itemize}[noitemsep,nolistsep,leftmargin=0.16cm]
                \item[] Programmer Analyst
                \item[] Maintained and improved UCF College of Medicine web applications
                    using {\bf C\#} and {\bf Razor}.
            \end{itemize}
			\begin{tabular}{p{3in} r}
				University of Central Florida, Orlando, FL & May 2014 - August 2014
			\end{tabular}
			\begin{itemize}[noitemsep,nolistsep,leftmargin=0.16cm]
				\item[] Computer Specialist
				\item[] Provided support to end users for laptop and desktop machines
						in a Windows and OS X environment. Repaired hardware and software
						issues.
			\end{itemize}

			\begin{tabular}{p{3in} r}
				Starwood Vacation Ownership, Orlando, FL & November 2012 - November 2013
			\end{tabular}
			\begin{itemize}[noitemsep,nolistsep,leftmargin=0.16cm]
				\item[] Application Development Internship
				\item[] Created applications for legacy business systems using the
						{\bf BBx} language as well as created business applications
						on the {\bf Salesforce} platform using {\bf Apex} code.
			\end{itemize}

\section{SKILLS}
			{\bf Programming Languages} - C, Java, C\#, BBx, Apex				\\
			{\bf Web Languages} - HTML5, CSS3, PHP, JavaScript, VisualForce	\\
			{\bf Operating Systems} - Linux, OS X, Windows

\section{EXPERIENCE}
            \begin{tabular}{p{3in} r}
                {\bf SpeakScript}
            \end{tabular}
            \begin{itemize}
                \item[] Helped design and test a custom programming language
                intended for spoken input into {\bf Google Glass} during a 24 hour
                hackathon. This language is compiled to {\bf JavaScript} and run natively on the device.\\
                https://github.com/UCF-HackFSU/SpeakScript}
            \end{itemize}
			\begin{tabular}{p{3in} r}
				{\bf NID Reset Application for Android}
			\end{tabular}
			\begin{itemize}
				\item[] Worked on the front end and of an {\bf Android} Application
						using {\bf Java} which simplified the process of students
						resetting their UCF Network ID Password.
			\end{itemize}
			\begin{tabular}{p{3in} r}
				{\bf Account Inforclosure Processing Tool}
			\end{tabular}
			\begin{itemize}
				\item[] Patched several business applications using the {\bf BBx}
						language to prevent users from processing accounts using
						tools meant for other accounts.
			\end{itemize}
			\begin{tabular}{p{3in} r}
				{\bf Business Workflow Wizards}
			\end{tabular}
			\begin{itemize}
				\item[] Created several wizards to streamline multiple department's
						workflows using the {\bf Apex} language for backend development
						and {\bf VisualForce} pages for the user-facing pages.
			\end{itemize}
			\begin{tabular}{p{3in} r}
				{\bf PhysicsWorld}
			\end{tabular}
			\begin{itemize}
				\item[] Participated in a 2-person 24-hour mini hackathon with the goal
						of creating a physics sandbox environment using {\bf HTML5},
						{\bf JavaScript}, and {\bf CSS3}. Made use of external
						libraries such as {\bf Paper.js}, {\bf JQuery}, and the
						\$1 Gesture Recognizer.
			\end{itemize}
			\begin{tabular}{p{3in} r}
				{\bf PL/0 Compiler}
			\end{tabular}
			\begin{itemize}
				\item[] Created a virtual machine, scanner, parser, and compiler for
						a tiny version of the Pascal programming language written in {\bf C}.
			\end{itemize}
%\section{ACTIVITIES}
%			Mobile Makers Club at UCF	\\
%			EXCEL Program Scholar

\end{resume}
\end{document}
